### 2016-11-02 main.tex
Actually submitted this version.
Some changes requested by the editor... not done yet.

The adult zebra finch ({\em Taeniopygia guttata}) sings a song made up
of 2--6 syllables, with longer songs taking on the order of a
second. The song may be repeated hundreds of times per day, is almost
identical each time, and several brain areas reflect this consistency
in highly stereotyped neural firing patterns. This consistency makes
the zebra finch one of the most popular models for the study of the
neural basis of learning, audition, and control.

@@

\begin{figure}
  % Width: 8, Height: 3, Fonts scale: 120%
  \includegraphics[width=\textwidth]{Fig1}
  \caption{This image was made by superposing the spectra of our 2818
    aligned songs.  Our example detection points, $t^*_1\ldots t^*_6$,
    are shown as red lines, with the recognition regions (30 ms
    $\times$ 1--8 kHz) marked as rectangles.}
  \label{fig:song}
\end{figure}

@@

Because the data set consists of temporally aligned songs, ground
truth is available for each song (albeit with minor variations due to
the alignment process used \cite{Poole2012}), and thus the detector
can be checked by presenting the recorded training songs as well as
the canonical detection events. To this end, besides the trained
network object, our learning code produces an audio file consisting of
all of the training data on the left audio channel and a delta
function at each aligned moment of target syllable presentation on the
right channel. Thus, when played on any audio player, the left channel
may be provided as input to the detector, and the the detector's
output pulses may be compared against the right channel.

@@

Mean latency is then given as the average time between the canonical
signal and the corresponding detection event.  It is a helpful number,
but not a critical one, since in zebra finch a detector with high but
constant latency can often be trained to trigger at a point somewhat
before the true moment of interest (for example, if triggering should
occur at the very beginning of a syllable, the detector's time window
may include previous syllable).  Often more important is the
variability in the latency.  We define jitter as the standard
deviation of the latency.

@@

The first two triggers, $t^*_1$ at 150 ms and $t^*_2$ at 200 ms, are
far from pure tones, but are closer to coloured noise.  They would be
difficult for a harmonic-stack filter bank to detect, and especially
to pinpoint in time.  $t^*_3$ (250 ms) and $t^*_6$ (400 ms) are rich
in overtones and contain downward slides with changing timbres.
$t^*_4$ (300 ms) occurs near the beginning of a more typical harmonic
stack amenable to a variety of recognition techniques, although
consistently detecting a point partway through the syllable demands a
detector that can use multiple time steps.  $t^*_5$ (350 ms) shows a
steady pitch followed by a complex changing tone structure.

>>>>

The adult zebra finch ({\em Taeniopygia guttata}) sings a song made up
of 2--6 syllables, with longer songs taking on the order of a
second. The song may be repeated hundreds of times per day, and is almost
identical each time.  Several brain areas reflect this consistency
in highly stereotyped neural firing patterns, which makes
the zebra finch one of the most popular models for the study of the
neural basis of learning, audition, and control.

@@

\begin{figure}
  % Width: 8, Height: 3, Fonts scale: 120%
  \includegraphics[width=\textwidth]{Fig1}
  \caption{The spectrogram of a typical song, used as the example
    throughout this paper.  This image was made by superposing the
    spectra of our 2818 aligned songs.  Our example detection points,
    $t^*_1\ldots t^*_6$, are shown as red lines, with the recognition
    regions (30 ms $\times$ 1--8 kHz) marked as rectangles.}
  \label{fig:song}
\end{figure}

@@

Because the data set consists of temporally aligned songs, the moment at which detection should occur during each song sample is available (albeit with minor variations due to
the alignment process used \cite{Poole2012}).  The detector
can be checked by comparing its response to the recorded training song samples against
these ``canonical'' detection events.  To this end, besides the trained
network object, our learning code produces an audio file consisting of
all of the training data on the left audio channel and a delta
function at each aligned moment of target syllable presentation on the
right channel. Thus, when played on any audio player, the left channel
may be provided as input to the detector, and the the detector's
output pulses may be compared against the right channel.

@@

We define latency as the time between the training target (during our tests, this is indicated by the canonical
signal in the test file) and the corresponding detection event.  It is a helpful number,
but not a critical one, since in zebra finch a detector with high but
constant latency can often be trained to trigger at a point somewhat
before the true moment of interest (for example, if triggering should
occur at the very beginning of a syllable, the detector may be trained to recognise the previous syllable and the gap thereafter).  Usually the variability in latency is the more important number.  We define jitter as the standard deviation of detection latency over the test songs.

@@

The first two triggers, $t^*_1$ at 150 ms and $t^*_2$ at 200 ms, are
far from pure tones, but are closer to bandpass-filtered white noise.  They would be
difficult for a harmonic-stack filter bank to detect, and especially
to pinpoint in time.  $t^*_3$ (250 ms) and $t^*_6$ (400 ms) are rich
in overtones and contain downward slides with changing timbres.
$t^*_4$ (300 ms) occurs near the beginning of a more typical harmonic
stack amenable to a variety of recognition techniques, although
consistently detecting a point partway through the syllable demands a
detector that can use multiple time steps.  $t^*_5$ (350 ms) shows a
steady pitch followed by a complex changing tone structure.
